---
title: "How-to-use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How-to-use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bulkfaker)
```

# Bulk_generator

Bulk_generator() function returns a list containing two data.frame : 
- *T* the Num.mixtures mixtures
- *P* the proportions used to build T

## Quick use
```{r, eval = FALSE}
# sc_counts a single cell dataset
# phenoData data.frame with information about matching cellType and cellID
pseudoBulk <- Bulk_generator(sc_counts, phenoData)
pseudoBulk$T #mixtures
pseudoBulk$P #proportions
```
Cells in sc_counts that did not match with phenoData cellID will not be used.
If no match or only one cellType, execution will be stopped.

## Remove cells from phenoData
```{r, eval = FALSE}
pseudoBulk <- Bulk_generator(sc_counts, phenoData, forbidden_CT = c("cell_type1","cell_type2"))
pseudoBulk$T #mixtures
pseudoBulk$P #proportions, cell_type1 and cell_types2 will be 0 for all mixtures
```

## Force all cell types in all mixtures
```{r, eval = FALSE}
pseudoBulk <- Bulk_generator(sc_counts, phenoData, nb_CT_random = FALSE)
pseudoBulk$T #mixtures
pseudoBulk$P #proportions, no 0 (except rounded ones)
```

## Other parameters

- Num.mixtures = 1000
- pool.size = 100
- min.percentage = 1
- max.percentage = 99
- seed = 24

